A Linear Solution of the Linearity Challenge

### 2025-12-24 paper/Permutations.lagda.tex
revised permutations

According to our nameless representation of channels, it is the \emph{order} of
channels in a typing context $\Context$ that determines the binding location in
the structure of a process. When the binding structure of a process changes, \eg
because a structural pre-congruence rule is applied, or when a channel
substitution occurs, \cf the right-hand side of the \LinkRule reduction, the
typing context must be suitably rearranged. Such rearrangement is in fact a
\emph{permutation} of the elements of $\Context$.

@@

The definition of \AgdaDatatype{\_↭\_} data type is nearly the same found in the
module \AgdaModule{Data.List.Relation.Binary.Permutation.Propositional} of
Agda's standard library. We have preferred defining our own notion of
permutation for improved simplicity and convenience: the
\AgdaInductiveConstructor{swap} constructor does not need a sub-permutation for
the tail of the typing context, which can always be performed, if needed, using
\AgdaInductiveConstructor{prep} and \AgdaInductiveConstructor{trans}. Also, and
more importantly, the data type is \emph{monomorphic} (it does not need to
relate lists of arbitrary type) and the quantified arguments $A$ and $B$ of
\AgdaInductiveConstructor{swap} and \AgdaInductiveConstructor{prep} are
implicit, which streamlines their usage in the rest of the code.

>>>>

According to our nameless representation of channels, it is the \emph{order} of
channels in a typing context $\Context$ that determines the binding location in
the structure of a process. When the binding structure of a process changes, \eg
because a structural pre-congruence rule is applied, or when a channel
substitution occurs, \cf the right-hand side of the \LinkRule reduction in
\Cref{tab:semantics}, the typing context must be suitably rearranged. Such
rearrangement is in fact a \emph{permutation} of the elements of $\Context$.

@@

The definition of \AgdaDatatype{\_↭\_} data type is nearly the same found in the
module \AgdaModule{Data.List.Relation.Binary.Permutation.Propositional} of
Agda's standard library. We have preferred defining our own notion of
permutation for improved simplicity and convenience: the
\AgdaInductiveConstructor{swap} constructor does not need a sub-permutation for
the tail of the typing context, which can always be performed, if needed, using
\AgdaInductiveConstructor{prep} and \AgdaInductiveConstructor{trans}. Also, and
more importantly, the data type is \emph{monomorphic} (it does not need to
relate lists of arbitrary type) and the quantified arguments $A$ and $B$ of
\AgdaInductiveConstructor{swap} and \AgdaInductiveConstructor{prep} can be made
implicit, which streamlines the usage of these constructors in the rest of the
code.
